\mytitle

### 2023-05-27 paper-seb-main.tex
Lots of simplifications to using multiple Latex files

@@

\vskip 1ex\newdimen\boxwidth
\boxwidth = \columnwidth
\advance\boxwidth by - 1em
\noindent\framebox[\columnwidth][r]{\parbox{\boxwidth}{\noindent\sf For the present paper, as a concrete example of this approach, the pilot survey analyzed \textbf{\the\dataN} papers with \textbf{\the\countAuthors} authors. The paper \textbf{\cite{ICmodel}}, discussed below in section \textbf{\ref{section-pandemic-modeling}}, relied on code composed of \textbf{\covidsimfiles} files, with over \textbf{\covidsimkLOC\ thousand} lines of code (how this compares with files in the survey is summarized in table \textbf{\ref{supplementaryTableRepoSummary}} in the \supplement).}}\vskip 1ex

@@

where the \the\countAuthors\ is the calculated number, save that line of text to a file, which is then import it into the paper where it is typeset in the normal way. Then, when and wherever the authors write the name \texttt{\textbackslash numberOfAuthors} in their paper's text, the typeset paper says \the\countAuthors, or whatever the actual value is at the time. Some easy \LaTeX\ coding can then present the numbers in the publisher's preferred style, such as \numbertoname 0, \numbertoname 1, \ldots\ \numbertoname 9, \numbertoname{10}, \numbertoname{11}, \ldots, \digitBlock{1000},  \digitBlock{1001}, etc, as done more realistically elsewhere in this paper (for instance, see footnote~\numbernamesexamplefootnote).

@@

\begin{tabular}{|lcl@{}cl@{\hskip 2em}cl|} \hline
\drop{\bfseries Data sources}&\lowarrow&\bfseries \drop{Models and analysis} & \lowarrow&\bfseries Select results& \lowarrow& \bfseries Submit for\\
\bfseries &&\bfseries & &\bfseries for write up & & \bfseries publication \\ \hline \hline 
&&&&&&\\
Experiments&& Hand calculations &&&&\\
Standard data&& Packages && Copy \& paste &&\\
Search engines&& SPSS etc & \bigBracket & and edit data && Final paper\\
Literature && Graphics packages  && (text, images, graphs, etc)&&\\
Sensors && Specially-written code, && into paper &&\\ 
&& \hskip 1em C, Python, R, Mathematica, etc  && && \\
\vdots && \vdots &&&& \\ &&&&&&\\ \hline
\end{tabular}\end{center}}\caption{A simplified schematic of the publication pipeline. For clarity, the pipeline has been linearized; in general, there will be repetitive cyclic iteration and refinement. The RAP and \RAPstar\ approaches encode the normally manual steps in the pipeline workflow so that they can be run automatically, and hence reproduce the results that underpin the final paper. The encoded \RAPstar\ algorithms can be shared with other scientists, scrutinized, simplified and optimized, and themselves turned into publishable objects --- they are scientific instruments, just like thermometers or DNA sequencers. Additional schematics are provided in section \ref{RAP-diagrams} in the \supplement.}
\label{fig-pipeline}
\end{table*}

@@

Spiegelhalter \cite{Spiegelhalter} says statistical information needs to be accessible, intelligible, assessable, and usable; he also suggests probing questions to help assess statistical quality (see \supplement\ section~\ref{supplementary-Spiegelhalter-section}). Results should not be uncritically accepted just because they are claimed. The skill and effort required to do statistics so it can be communicated clearly and correctly, as above, is not to be taken for granted; in fact, there is widespread concern about the poor quality of statistics in science \cite{paul-hci,pnas-stats}. While it is assumed that statistics should be peer-reviewed, and that review will often lead to improvement, critical papers like \cite{paul-hci,pnas-stats} show that reviewers and editors are often failing to pick up on poor statistics.

@@

Some authors assert that the purpose of code is to provide insight into models, rather than precise (generally numerical) analyses summarizing data or properties of the data \cite{assessing-quality}. In reality, if code is inadequate, any so-called ``insights'' will be potentially flawed, and flawed in unknown ways. Indeed, none of the papers sampled (described in \supplement\ section~\ref{survey-section}) claimed their papers were using code for insight; all papers claimed, explicitly or implicitly, that their code outputs were integral to their peer-reviewed results.

@@

%An example is the documentation at the code repository \cite{BayesWaveCode}, which requires three high-profile \emph{{Physics Review D}} papers \cite{BayesWave1,BayesWave2,BayesWave3} be cited to acknowledge any use, but only one of them, \cite{BayesWave3}, mentions the code, and even then it fails to acknowledge the contributions of its 10 programmers (despite 6 being co-authors). The paper does cite the repository URL, but unlike the papers it cites conventionally, it omits all the code's authors. Acknowledgement does not seem to matter, even to the people who did the work.

@@

Program code contains data. Almost all code contains ``magic numbers'' --- that is, data masquerading as code (see \supplement, section \ref{on-code-data-publication}). This common practice ensures that published data is rarely all of the relevant data because it omits the magic numbers embedded in the code. Such issues emphasize the need for repositories to require the inclusion of code so all data, including that embedded in the code, is actually available.

@@

Although convenience and convention treat data and code differently, ultimately, data and code are formally equivalent (see \supplement, section \ref{on-code-data-publication}) in the important sense that there is no pre-determined boundary between them or formal criteria to distinguish them: different scientific projects can draw their boundaries differently and as they see best fits their work. Indeed, all of the papers reviewed here where code was available include critical data in their code. It therefore makes no sense to have separate rules for data and code --- except in the most trivial cases \emph{both\/} are equally essential for verification, building on, and reproduction of work.

@@

\label{mentionPLOSandIEEE}
Journal policies could start to explicitly encourage computationally reproducible science using RAP and \RAPstar\ techniques. That is, the research's methodology itself may be a mixture of data and code. As this paper's \supplement\ shows in section \ref{restrictive-policies}, many journals (e.g., \emph{PLOS ONE\/} and, ironically, \emph{IEEE Transactions on Software Engineering\/}) and repositories have policies that make RAP much harder or just counter-productive at the last step.

@@

Compare the discussion here with figure \ref{excelFigure}, in a series of figures in the \supplement, which illustrates the problem as it presents in many scientific papers.

@@

\dataaccess{There is an extended discussion of the methodology of this paper in the \supplement, section \ref{on-code-data-publication}. The \supplement\ also presents all raw data in tabular form. All material is also available for download at \url{github.com/haroldthimbleby/Software-Enginering-Boards},\footnote{\color{red}This is a temporary URL before meeting publication repository requirements for accepted papers.\color{black}} which has been tested in a clean build, etc.

>>>>

\makeatletter
      \input paper-seb-supplementary-material.aux 
\makeatother

@@

\vskip 1ex\newdimen\boxwidth
\boxwidth = \columnwidth
\advance\boxwidth by - 1em
\noindent\framebox[\columnwidth][r]{\parbox{\boxwidth}{\noindent\sf For the present paper, as a concrete example of this approach, the pilot survey analyzed \textbf{\the\dataN} papers with \textbf{\the\countAuthors} authors. The paper \textbf{\cite{ICmodel}}, discussed below in section \textbf{\ref{section-pandemic-modeling}}, relied on code composed of \textbf{\covidsimfiles} files, with over \textbf{\covidsimkLOC\ thousand} lines of code (how this compares with files in the survey is summarized in table \textbf{\ref{supplement-table-repo-summary}} in the \supplement).}}\vskip 1ex

@@

where the \the\countAuthors\ is the calculated number, save that line of text to a file, which is then import it into the paper where it is typeset in the normal way. Then, when and wherever the authors write the name \texttt{\textbackslash numberOfAuthors} in their paper's text, the typeset paper says \the\countAuthors, or whatever the actual value is at the time. Some easy \LaTeX\ coding can then present the numbers in the publisher's preferred style, such as \numbertoname 0, \numbertoname 1, \ldots\ \numbertoname 9, \numbertoname{10}, \numbertoname{11}, \ldots, \digitBlock{1000},  \digitBlock{1001}, etc, as done more realistically elsewhere in this paper (for instance, see footnote \ref{name-example-footnote}).

@@

\begin{tabular}{|lcl@{}cl@{\hskip 2em}cl|} \hline
\drop{\bfseries Data sources}&\lowarrow&\bfseries \drop{Models and analysis} & \lowarrow&\bfseries Select results& \lowarrow& \bfseries Submit for\\
\bfseries &&\bfseries & &\bfseries for write up & & \bfseries publication \\ \hline \hline 
&&&&&&\\
Experiments&& Hand calculations &&&&\\
Standard data&& Packages && Copy \& paste &&\\
Search engines&& SPSS etc & \bigBracket & and edit data && Final paper\\
Literature && Graphics packages  && (text, images, graphs, etc)&&\\
Sensors && Specially-written code, && into paper &&\\ 
&& \hskip 1em C, Python, R, Mathematica, etc  && && \\
\vdots && \vdots &&&& \\ &&&&&&\\ \hline
\end{tabular}\end{center}}\caption{A simplified schematic of the publication pipeline. For clarity, the pipeline has been linearized; in general, there will be repetitive cyclic iteration and refinement. The RAP and \RAPstar\ approaches encode the normally manual steps in the pipeline workflow so that they can be run automatically, and hence reproduce the results that underpin the final paper. The encoded \RAPstar\ algorithms can be shared with other scientists, scrutinized, simplified and optimized, and themselves turned into publishable objects --- they are scientific instruments, just like thermometers or DNA sequencers. Additional schematics are provided in section \ref{supplement-RAP-diagrams} in the \supplement.}
\label{fig-pipeline}
\end{table*}

@@

Spiegelhalter \cite{Spiegelhalter} says statistical information needs to be accessible, intelligible, assessable, and usable; he also suggests probing questions to help assess statistical quality (see \supplement\ section~\ref{supplement-Spiegelhalter-section}). Results should not be uncritically accepted just because they are claimed. The skill and effort required to do statistics so it can be communicated clearly and correctly, as above, is not to be taken for granted; in fact, there is widespread concern about the poor quality of statistics in science \cite{paul-hci,pnas-stats}. While it is assumed that statistics should be peer-reviewed, and that review will often lead to improvement, critical papers like \cite{paul-hci,pnas-stats} show that reviewers and editors are often failing to pick up on poor statistics.

@@

Some authors assert that the purpose of code is to provide insight into models, rather than precise (generally numerical) analyses summarizing data or properties of the data \cite{assessing-quality}. In reality, if code is inadequate, any so-called ``insights'' will be potentially flawed, and flawed in unknown ways. Indeed, none of the papers sampled (\supplement\ section~\ref{supplement-survey-section}) claimed their papers were using code for insight; all papers claimed, explicitly or implicitly, that their code outputs were integral to their peer-reviewed results.

@@

%An example is the documentation at the code repository \xcite{BayesWaveCode}, which requires three high-profile \emph{{Physics Review D}} papers \xcite{BayesWave1,BayesWave2,BayesWave3} be cited to acknowledge any use, but only one of them, \xcite{BayesWave3}, mentions the code, and even then it fails to acknowledge the contributions of its 10 programmers (despite 6 being co-authors). The paper does cite the repository URL, but unlike the papers it cites conventionally, it omits all the code's authors. Acknowledgement does not seem to matter, even to the people who did the work.

@@

Program code contains data. Almost all code contains ``magic numbers'' --- that is, data masquerading as code (see \supplement, section \ref{supplement-on-code-data-publication}). This common practice ensures that published data is rarely all of the relevant data because it omits the magic numbers embedded in the code. Such issues emphasize the need for repositories to require the inclusion of code so all data, including that embedded in the code, is actually available.

@@

Although convenience and convention treat data and code differently, ultimately, data and code are formally equivalent (see \supplement, section \ref{supplement-on-code-data-publication}) in the important sense that there is no pre-determined boundary between them or formal criteria to distinguish them: different scientific projects can draw their boundaries differently and as they see best fits their work. Indeed, all of the papers reviewed here where code was available include critical data in their code. It therefore makes no sense to have separate rules for data and code --- except in the most trivial cases \emph{both\/} are equally essential for verification, building on, and reproduction of work.

@@

\label{mentionPLOSandIEEE}
Journal policies could start to explicitly encourage computationally reproducible science using RAP and \RAPstar\ techniques. That is, the research's methodology itself may be a mixture of data and code. As this paper's \supplement\ shows in section \ref{supplement-restrictive-policies}, many journals (e.g., \emph{PLOS ONE\/} and, ironically, \emph{IEEE Transactions on Software Engineering\/}) and repositories have policies that make RAP much harder or just counter-productive at the last step.

@@

Compare the discussion here with figure \ref{supplement-fig:excel}, in a series of figures in the \supplement, which illustrates the problem as it presents in many scientific papers.

@@

\dataaccess{There is an extended discussion of the methodology of this paper in the \supplement, section \ref{supplement-on-code-data-publication}. The \supplement\ also presents all raw data in tabular form. All material is also available for download at \url{github.com/haroldthimbleby/Software-Enginering-Boards},\footnote{\color{red}This is a temporary URL before meeting publication repository requirements for accepted papers.\color{black}} which has been tested in a clean build, etc.
